% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{}

\begin{document}

\hypertarget{scoping-brief-real-time-crypto-volatility-detection}{%
\section{Scoping Brief: Real-Time Crypto Volatility
Detection}\label{scoping-brief-real-time-crypto-volatility-detection}}

\textbf{Author:} Rizaldy Utomo\\
\textbf{Prediction horizon:} 60 seconds\\
\textbf{Primary metric:} PR-AUC

\hypertarget{use-case}{%
\subsection{Use Case}\label{use-case}}

This project detects short-horizon volatility spikes in major crypto
pairs using public Coinbase market data. The operational goal is not
automated trading. The goal is to surface periods when market conditions
become materially more unstable over the next minute so the stream can
support monitoring, alerting, and downstream risk-aware analytics.

\hypertarget{prediction-goal}{%
\subsection{Prediction Goal}\label{prediction-goal}}

At every one-second feature window, the model predicts whether the next
60 seconds will exhibit unusually high realized volatility. The output
is a probability score plus a thresholded binary label.

The dashboard exposes that prediction in two ways: - an orange-dot
marker when the model flags a live spike - a plain-language turbulence
outlook that translates the short-horizon signal into a simple ``rougher
vs calmer'' reading for the next minute, hour, and day, similar to the
live odds of a yes-or-no question about whether conditions will get
rougher

\hypertarget{success-metric}{%
\subsection{Success Metric}\label{success-metric}}

The primary evaluation metric is \textbf{PR-AUC} because volatility
spikes are relatively rare compared with normal market conditions. F1 at
the selected validation threshold is tracked as a supporting metric.

\hypertarget{risks-and-assumptions}{%
\subsection{Risks And Assumptions}\label{risks-and-assumptions}}

\begin{itemize}
\tightlist
\item
  Public WebSocket data may contain temporary gaps, reconnects, or
  bursty update cadence.
\item
  Two-product scope (\texttt{BTC-USD}, \texttt{ETH-USD}) is sufficient
  for the first assignment pass.
\item
  Labels are derived from future realized volatility, so training data
  must be strictly time-ordered and leakage-aware.
\item
  A lightweight logistic baseline is sufficient for the first graded
  implementation.
\item
  All infrastructure runs locally through Docker Compose for
  reproducibility.
\end{itemize}

\end{document}
